A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-01-22 manuscript.Rmd
should we add a checklist @brandmaier?
add introduction

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: pdf_document
repro:
  packages:
    - usethis
    - repro
---

<!-- the HTML comments, like this one, are meta comments, mainly describing the intent --->
<!-- each sentence below a heading summarizes what I want to say there --->
<!-- "Hands-on:" means concrete practical application, they roughly proceed from easy/familiar to hard/unfamiliar-->

@@

<!-- define reproducibility -->

## Productivity

<!-- lure the reader in -->

Adherence to best practices promises to increase productivity for individual researchers and the community as a whole.

## Metascientific Arguments

<!-- present reproducibility as something that fits right into the researchers' objectives-->

Reproducibility is caused by openness, enables replication, and all three together warrant trust in science.

@@

### Data Integrety (optional)

@@

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: pdf_document
repro:
  packages:
    - usethis
    - repro
    - here
---

<<!-- the HTML comments, like this one, are meta comments, mainly describing the intent --->
<!-- each sentence below a heading summarizes what I want to say there --->
<!-- "Hands-on:" means concrete practical application, they roughly proceed from easy/familiar to hard/unfamiliar-->

```{r setup, include=FALSE}
library(repro)
source(here::here("R", "link.R"))
```

@@

<!-- define reproducibility -->
<!-- is a direct quote from my master thesis -->
<!-- I wouldn't want to cite it. @brandmaier, would you please rewrite? -->
A reproducible scientific product allows other researchers to obtain the same results from the same dataset in a way that enables substantive criticism and therefore facilitates replication.
<!-- lure the reader in -->
This notion of independent verifiability has long been part of "good scientific practice", but has not reached its full potential to benefit the scientific community.
<!-- expand: who is calling it a requirement, maybe metascientific arguments-->
Reproducing an empirical study is often tedious and frustrating work for the researcher.
However, if reproduction would require mere minutes instead of hours, it could greatly facilitate collaboration within and across research projects.
<!-- Guiding principle: spending machine compute time instead of human research time -->
To archive this boost, we must place the burden of reproducing something upon computers instead of human researchers.
A scientific document should therefore be understood by researchers but reproduced by computers.

This tutorial walks through the creation of such a document that can be reproduced automatically.
Though reproducibility is but a small part of the research process, it can serve as the mortar of open science building blocks (e.g. preregistration, open data, postpublication review).
Therefore, we show the whole lifecycle of an open research project, where some parts are essential to archive reproducibility.
Still, the reader can safely skip sections marked as optional, when unfit for their research question or methods.
However, any empirical data analysis will suffer from the following threats to reproducibility:
<!-- Which problems are solved by which tool (like in Andreas talk)-->
<!--stolen from: https://brandmaier.github.io/reproducible-data-analysis-materials/KULeuvenQuantPsy2020.html#11 -->

1. Multiple versions of scripts/data (e.g., dataset has changed over time, i.e., was further cleaned or extended)
2. Copy&paste errors (e.g., inconsistency between reported result and reproduced result)
3. unclear which scripts should be executed in which order
4. Broken software dependencies (e.g., analysis broken after update, missing package)

It is common to rely on the craftiness of the researcher to debug these problems, but we could prevent them altogether with:

1. Version control
2. Dynamic document creation
3. Dependency tracking
4. Software management

We deem each concept necessary to archive longterm reproducibility.
However, the tools you use to archive them are a mere matter of taste and project requirements.
This tutorial will follow the recommendations of @peikertMissing and utilizes Git for version control, RMarkdown for dynamic document creation, Make for dependency tracking and Docker for software management.
Their interplay is shown in Figure \@ref(fig:schematic).
At several points we suggest other viable alternatives.

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components (in dashed boxes) central to the reproducible workflow: version control (git), dependency management (Make), containerization (Docker), and dynamic document generation (R Markdown). Git tracks changes to the project over time. Make manages dependencies among the files. Docker provides a container, in which the final report is built using dynamic document generation in R Markdown. Reproduced from @peikertMissing  "}
# file gets downloaded in Makefile
knitr::include_graphics("images/nutshell.svg", auto_pdf = TRUE)
```

@@

### Data Integrity (optional)

@@

## Checklist

<!-- Should we design a checklist? -->`
